---
title: "TidyTemplate"
date: 2022-01-19
output: html_output
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

library(glue)

library(tidymodels)
library(themis)

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2022-01-18")

chocolate <- tt$chocolate

```

# Wrangle

```{r Wrangle}
 
## Tidy up the dataset by
# - separating the ingredients column to get the number of ingredients and the ingredients
# - converting chracter variables to numericals
# - changing the ingredient code to the proper name
# - Hot encoding the ingredients (For ML purposes)

ingredients <- tribble(
  ~code , ~ingredient,
  ####################
  "B", "Beans",
  "S", "Sugar",
  "S*", "Sweetener",
  "C", "Cocoa Butter",
  "V", "Vanilla",
  "L","Lecithin",
  "Sa","Salt"
)

chocolate_tidy <- chocolate %>% 
  separate(ingredients, into = c("no_ingredients","contents"), sep = "-") %>% 
  mutate_at(c("no_ingredients","contents"), str_squish) %>% 
  mutate_at(c("no_ingredients","cocoa_percent"), parse_number) %>% 
  rowid_to_column() %>% 
  separate_rows(contents, sep = ",") %>% 
  left_join(ingredients, by = c("contents" = "code")) %>% 
  select(-contents) %>% 
  mutate(val = 1) %>% 
  pivot_wider(names_from = ingredient, values_from = val, values_fill = 0) %>% 
  select(-rowid)
```

```{r}

## Getting the top and least most memorable characteristics from the data
top_used_xtics <- chocolate_tidy %>% 
  select(most_memorable_characteristics) %>% 
  separate_rows(most_memorable_characteristics, sep = ",") %>% 
  mutate(most_memorable_characteristics = str_squish(most_memorable_characteristics) %>% 
           str_to_lower()) %>% 
  count(most_memorable_characteristics, sort = T) %>% 
  slice_max(order_by = n, prop = .05) %>% 
  pull(most_memorable_characteristics)

top_used_xtics <- glue_collapse(top_used_xtics, sep = "|")

least_used_xtics <- chocolate_tidy %>% 
  select(most_memorable_characteristics) %>% 
  separate_rows(most_memorable_characteristics, sep = ",") %>% 
  mutate(most_memorable_characteristics = str_squish(most_memorable_characteristics) %>% 
           str_to_lower()) %>% 
  count(most_memorable_characteristics, sort = T) %>% 
  slice_min(order_by = n, prop = .05, with_ties = F) %>% 
  pull(most_memorable_characteristics)

least_used_xtics <- glue_collapse(least_used_xtics, sep = "|")

```

```{r}

## Adding an extra feature to the dataset to see if either the top / least used xtics were included 
chocolate_tidy <- chocolate_tidy %>% 
  mutate(top_used_xtics = str_detect(most_memorable_characteristics, top_used_xtics) %>% as.integer(),
         least_used_xtics = str_detect(most_memorable_characteristics, least_used_xtics) %>% as.integer()) %>% 
  janitor::clean_names()
```


## Visualization
```{r}
ratings_by_country <- chocolate %>% 
  mutate(company_location = case_when(
    company_location %in% c("U.S.A.","U.K.") ~ str_remove_all(company_location,"\\."),
    company_location == "U.A.E." ~ "United Arab Emirates",
    company_location == "St. Lucia" ~ "Saint Lucia",
    company_location == "St.Vincent-Grenadines" ~ "Saint Vincent",
    TRUE ~  str_to_title(company_location))) %>% 
  count(company_location, wt = mean(rating))
           

(rating_map <- map_data(map = "world") %>% 
  left_join(ratings_by_country, by = c("region" = "company_location")) %>% 
  ggplot(aes(long, lat)) +
  geom_polygon(aes(group = group, fill = n),col = "white") +
  scale_fill_viridis_c() +
  ggthemes::theme_map() +
  labs(
    title = "Average Chocolate rating by location of company",
    subtitle = "Countries that are not represented in this data are colored in Grey",
    fill = "Avg. Rating",
    caption = "Data:Flavors of Cacao | Plot: Haanuel_NG"
  ) +
  theme(
    plot.title = element_text(size = 16)
  ))
```

# Notes
- 45% of companies in this data are in the USA

# Model Development
The goal is to predict if a rating is above or below 3 

```{r Model}

chocolate_tidy <- chocolate_tidy %>% 
  mutate(rating_bucket = ifelse(rating > 3, "above", "below")) 

set.seed(1342)

chocolate_split <- initial_split(chocolate_tidy, strata = rating_bucket)
chocolate_train <- training(chocolate_split)
chocolate_folds <- vfold_cv(chocolate_train, strata = rating_bucket)

```

## Creating Recipe
```{r}
chocolate_rec <- recipe(rating_bucket~., data = chocolate_train) %>% 
  step_rm(ref,company_manufacturer,review_date,most_memorable_characteristics,rating,specific_bean_origin_or_bar_name, no_ingredients, company_location, country_of_bean_origin) %>% 
 # step_other(company_location, country_of_bean_origin) %>% 
  step_normalize(cocoa_percent) %>% 
 # step_dummy(company_location, country_of_bean_origin) %>% 
  step_zv(all_predictors()) %>% 
  step_corr(all_numeric_predictors()) %>% 
  step_downsample(rating_bucket)
```

## Model Specification
```{r}
ranger_spec <- rand_forest(min_n = tune(),mtry = tune(), trees = tune()) %>% 
  set_engine("ranger") %>% 
  set_mode("classification")

ranger_workflow <- workflow() %>% 
  add_recipe(chocolate_rec) %>% 
  add_model(ranger_spec)

chocolate_grid <- crossing(
  min_n = c(11, 31),
  mtry = c(4),
  trees = c(1001, 2001))

grid_latin_hypercube(min_n(), trees())

metrics_ <- metric_set(accuracy, roc_auc, sens, spec)

```

## Model Tuning
```{r}
doParallel::registerDoParallel()

ranger_tune <- tune_grid(
  ranger_workflow,
  resamples = chocolate_folds,
  grid = chocolate_grid,
  metrics = metrics_,
  control = control_grid(verbose = TRUE, save_pred = TRUE, save_workflow = TRUE))

doParallel::stopImplicitCluster()
```

## Model Exploration
```{r}
autoplot(ranger_tune)

show_best(ranger_tune, "roc_auc")

final_ranger_wf <- ranger_workflow %>% 
  finalize_workflow(select_best(ranger_tune, "roc_auc"))
```

## Fitting Model
```{r}
doParallel::registerDoParallel()

last_fit_ <- last_fit(final_ranger_wf, chocolate_split, metrics = metrics_)

doParallel::stopImplicitCluster()
```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# ggsave(
#   "2022-01-18/rating_map.png",
#   plot = rating_map,
#   device = ragg::agg_png(
#     width = 15,
#     height = 9,
#     units = "in",
#     scaling = 1.2,
#     res = 720
#   )
# )

```
