---
title: "TidyTemplate"
date: 2022-01-25
output: html_output
---

# TidyTuesday


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggtext)
library(showtext)


font_add_google(name = "quicksand",  family = "quicksand")

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2022-01-25")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r}
## Function to pull game name after feeding it a decade and rating
extract_name <- function(decade_x, rating){
  
  ratings %>% 
  filter(year %in% c(1900:2021)) %>% 
  mutate(decade = 10 * (year %/% 10),
         decade = factor(decade)) %>% 
  filter(decade == decade_x, average == rating) %>% 
  select(name) %>% 
  pull()
  
}

```


```{r Wrangle}

ratings <- tt$ratings

## Preparing data for plotting

(ratings_by_decade <- ratings %>% 
  filter(year %in% c(1900:2021)) %>% 
  mutate(decade = 10 * (year %/% 10)) %>% 
  select(decade, average) %>% 
  group_by(decade) %>% 
  summarize(n = n(),
            highest = max(average),
            lowest = min(average), .groups = "drop") %>% 
  mutate(decade = factor(decade)) %>% 
  mutate(name_h = map2_chr(decade, highest, extract_name),
         name_l = map2_chr(decade, lowest, extract_name)) %>% 
  mutate(n = format(n, big.mark=",",scientific=FALSE) %>% str_squish(),
         y_axis = glue::glue("**{decade}s** (n={n})")) )

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

showtext_auto()

(board_games_plot <- ratings_by_decade %>% 
    
  ggplot() +
    
  geom_vline(xintercept = 0, colour = "gray80") +
  geom_vline(xintercept = 2.5, colour = "gray80") +
  geom_vline(xintercept = 5.0, colour = "gray80") +
  geom_vline(xintercept = 7.5, colour = "gray80") +
  geom_vline(xintercept = 10, colour = "gray80") +
    
  geom_segment(aes(x = lowest, xend = highest, y = y_axis, yend = y_axis), col = "#C2C23A", size = 0.8) +
  geom_point(aes(lowest,y_axis), col = "#124F7A", size = 3) +
  geom_point(aes(highest,y_axis), col = "#BF1111", size = 3) +
  
  geom_text(aes(lowest,y_axis, label = name_l), vjust = 0, nudge_y = 0.3, size = 2.4, fontface = "bold", family = "quicksand") +
  geom_text(aes(highest,y_axis, label = name_h), vjust = 0, nudge_y = 0.3, size = 2.4, fontface = "bold", family = "quicksand") + 
  
  scale_x_continuous(limits = c(0,10)) +
  
  labs(
    title = "**Board games ratings by decade**",
    subtitle = "Board games with the <span style = 'color:#124F7A;'>lowest</span> and <span style = 'color:#BF1111;'>highest</span> average rating by decade, published bewteen 1900 and 2021",
    x = "Average Rating",
    y = "Decade",
    caption = "\nData: Kaggle by way of Board Games Geek, with a hattip to David and Georgios\n\nPlot: Orignal Plot made by Lee Olney, recreated by Emmanuel Ugochukwu"
  ) +
  
  theme_minimal() +
  
  theme(text = element_text(family = "quicksand") ,
        plot.title = element_markdown(hjust = 0.5),
        plot.subtitle = element_markdown(size = 10, hjust = 0.5),
        axis.text.y = element_markdown(hjust = 0),
        axis.ticks = element_blank(),
        axis.line.y = element_blank(),
        axis.text = element_markdown(),
        axis.title = element_text(size = 7),
        plot.caption = element_text(size = 7, hjust = 1)))
  
```



# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  "board_games.png",
  plot = board_games_plot,
  device = ragg::agg_png(
    width = 15,
    height = 9,
    units = "in",
    scaling = 1.2,
    res = 720
  )
)

```
